Holographic duality beyond AdS/CFT

### 2021-12-08 alpha/BeyondAdSCFT/beyondAdS.tex
Add TTbar updates from John & minor stuff

@@

\subsection{$T\bar{T}$ deformation}
In a Lorentzian invariant theory, the stress tensor $T^{\mu\nu}$ is conserved, i.e. $\partial_\mu T^{\mu\nu}=0$. One can define its determinant $\text{Det} T_{\mu\nu}$ as 
\begin{equation}
\begin{split}
    \mathcal O_{T\bar T}&:= \text{Det} T_{\mu\nu} \\
    &=T_{xx}T_{\bar x\bar x}-T_{x\bar x}T_{\bar{x} x} \\
    &=\text{Lim}_{x \rightarrow y} (T_{xx}(x)T_{\bar x\bar x}(y)-T_{x\bar x}(x)T_{\bar{x} x}(y) )+ \text{derivatives}
    \end{split}
\end{equation}
which is well-defined, and has 
\begin{equation}
    \langle n| \mathcal{O}_{T\bar T} |\rangle =\langle n| T |n\rangle \langle n|\bar T |n\rangle -\langle n| 
    \Theta|n\rangle \langle n|\bar{\Theta} |n\rangle
\end{equation}

>>>>

\subsubsection{The worldsheet \cft{2}}

@@

\eq{D(x,\bar x)=\int d^2z (\partial_x J \partial_x+2\partial_x^2J)(\partial_{\bar{x}} \bar{J} \partial_{\bar{x}}+2\partial_{\bar{x}}^2\bar{J}) \Phi_1}

\eq{A^a(x,\bar{x})=\int d^2z k^a(z)(\partial_{\bar{x}} \bar{J} \partial_{\bar{x}}\Phi_1+2\partial_{\bar{x}}^2\bar{J}\Phi_1)}

The dual spacetime CFT at large $p$ is argued to be the symmetric product orbifold $\mathcal{M}^p/S_p$, denoting the seed theory $\mathcal{M}$, the energy-momentum tensor can be written as 
\eq{T(x)=\sum_{i=1}^p T_i(x)}

which can be also written as 
\eq{T(x)=\frac1{2k}(\partial_x J\partial_x \Phi_1+2\partial_x^2 J\Phi_1)\bar{J}(\bar{x};\bar{z})}

The OPEs are 
\eq{T(x, \bar{x}) D(y, \bar{y})\sim \frac{c_{\mathcal{M}}}{(x-y)^4}\bar{T}(\bar{y})+\cdots}

\subsection{\TTbar deformation}
In a Lorentzian invariant theory, the stress tensor $T^{\mu\nu}$ is conserved, i.e. $\partial_\mu T^{\mu\nu}=0$. One can define its determinant $\text{Det} T_{\mu\nu}$ as 
\begin{equation}
\begin{split}
    \mathcal O_{T\bar T}&:= \text{Det} T_{\mu\nu} \\
    &=T_{xx}T_{\bar x\bar x}-T_{x\bar x}T_{\bar{x} x} \\
    &=\text{Lim}_{x \rightarrow y} (T_{xx}(x)T_{\bar x\bar x}(y)-T_{x\bar x}(x)T_{\bar{x} x}(y) )+ \text{derivatives}
    \end{split}
\end{equation}
which is well-defined, and has 
\begin{equation}
    \langle n| \mathcal{O}_{T\bar T} |\rangle =\langle n| T |n\rangle \langle n|\bar T |n\rangle -\langle n| 
    \Theta|n\rangle \langle n|\bar{\Theta} |n\rangle
\end{equation}
